Alleviating the Topology Mismatch Problem in Distributed Overlay Networks

### 2014-11-30 structured.tex
2014.11.30 (Vassilis) Structured section massively reworked. Clean-up, rewording and reviewing comments from Alex. Removed Cone algorithm as its text was badly written and the paper was equaly badly written. New reference added (.bib file updated and KK2000.pdf file added).

This section offers description and analysis of algorithms proposed
to address the topology mismatch problem in structured \p\ networks. 
The categorization of the approaches is based on how different
levels of proximity information is gathered as well as  
the way peer routing tables are maintained and used in an effort make hops in
overlays as efficient as possible. 
%%AD what does it really mean this below???
The categorization is based on previous work found in the
literature~\cite{CDHR2002,CDCR2002,RSS2002}.

%%COMM Rephrased as above to keep it analogous to the opening paragraph of
%% the unstructured part.
%%
% This section presents a description and analysis of algorithms proposed
% to address the topology mismatch problem in structured \p\ networks.
% In structured \p\ networks, the construction of the routing tables
% held by participating nodes determines the efficiency of message forwarding.
% Routing tables that closely match the underlying IP topology
% achieve increased performance. As a result, the proposed solutions for
% the topology mismatch problem for structured \p\ networks
% use different levels of proximity
% information to optimize the routing tables used by peers.
% The categorization of the algorithms we present here is based on the
% categorization suggested by previous
% work~\cite{CDHR2002,CDCR2002,RSS2002}.

@@

\emph{Global Soft-State} \cite{XTZ2003} builds a global map to help
choose shorter routing paths. This is accomplished by 
combining the landmark binning method with small
scale distance probes to reveal the proximity properties 
of the underlying network. 
%Figure \ref{fig:global_softstate} presents the landmark
%space and the mapping of the position of the nodes.
This global view of the state is made available to 
\emph{all} nodes to help them find the best way to route their messages. 
%%AD when you say "all" above means what?? all in the structured network?? 
%%	how is the structured network organized?  (a line or 2 for this?)
\emph{Global Soft-State} operates in $2$ phases:
\emph{generation} and \emph{use} of the proximity information. 
For \emph{generating} the proximity information, 
a hybrid approach is proposed: it uses landmark clustering as a
preprocessing step to select a number of potential nearest neighbor
candidates and then, refines the selection by incorporating a
round-trip-time-based scheme to ultimately choose the closest node. 
The algorithm follows a different path from that of the
classic gossiping approaches for the construction and 
maintenance of the overlay when 
it comes to \emph{use} the proximity information.
%%AD isn't the following sentence somewhat of repetition??? (of what 
%%	is stated above?? 
The approach is based on landmark clustering 
for generation and strategic
placement of proximity information on the overlay. 
This information is called a ``map'' and concerns a 
region of the overlay; 
the latter may be part of the Cartesian space in
structures like \emph{eCAN}~\cite{xu_ecan_2002} or 
a set of nodes sharing a particular
prefix in overlays such as \emph{Pastry}\cite{antony_pastry_2001}. 
Thus, each node not only can access such information from 
these landmarks but can also subscribe to
relevant \emph{soft states} and get notified on dynamic network changes. 
A node may appear in a maximum of $log(N)$ such maps.
Although this approach does reduce the routing latency to far nodes, it
can become expensive as it is 
possible to end up with a very large number of regions
each of which has to maintain a map. 
The fact that a peer may appear in multiple
such maps points into additional traffic for probing and notifications
and so renders the approach not scalable \cite{RGJZ2004}. 
Moreover, to refine measurements
additional inner-bin measurements are needed~\cite{WZS2004}.
Also, improvements within a region can be minimal as there exists
limited knowledge about neighboring zones.
%%AD rephrased what is below -2 lines- as above..
% Also improvement
% is done within a region because of little knowledge about neighboring zones.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% COMM Removed most of the paragraph below which 
%%		contains info that we cannot back
%% Rescanned papers and wrote the paragraph below.
%% DO NOT PERMANENTLY DELETE!
% Unfortunately, maintained of several host states at different layers,
% renders any content migration a costly process. Additionally, the method does
% not make any continuing effort to remap
% the overlay structure after nodes successfully join resulting into poor
% adaptation to changing conditions. Although this approach greatly reduces the
% routing latency to far nodes, it is unable to dynamically identify nodes that
% are close to routers and gateways in order to construct the secondary overlay.
% Nevertheless, static recognition of such nodes is currently done based on BGP
% reports and pre-chosen landmarks, sacrificing the self-organizing attribute of
% traditional DHTs.
% Xu \textit{et al.} \cite{XTZ2003} state that there are three ways
% generating proximity information
%\begin{itemize}
% \item Expanding Ring Search\\
%Expanding ring search can be of two forms. First it can utilize the multi-cast
%infrastructure in the underlying network in order to emit its messages.
%Unfortunately such infrastructures are not widely deployed thus the
%implementations of this way of generating proximity information is limited to
%blindly flooding the neighborhood to obtain reasonable results.
% \item Heuristics\\
%Heuristics are used in order to reduce the blindness of the expanding ring
%search and make realizations more efficient and effective. Unfortunately a
%common problem of all heuristic approaches is the local minimum pitfall in
%which
%the search might be caught into.
% \item Landmark Binning\\
%Landmark clustering is based on the view that nodes with similar distances to a
%set of predefined well-known landmark nodes are pretty likely of being close to
%each other. But this approach has its weaknesses as well, such as the fact that
%is a rather coarse grained approximation, therefore not particularly well
%suited
%for differentiating nodes within close distance to each other.
%\end{itemize}
% TODO: IN PAPER INTRODUCTION A DISCUSSION ABOUT
%TOPOLOGY-AWARE CAN
%Techniques to exploit topology information in overlay
%routing include geographic layout, proximity routing and
%proximity neighbor selection [3]. With geographic layout
%such as topology-aware CAN [12], the overlay structure is
%constrained by underlying network topology. This tech-
%nique, unfortunately, can create uneven distribution of
%nodes in the overlay, increasing the chances of overloading
%nodes and rendering the maintenance cost formidable. Our
%study shows that, for a typical 10,000-node topology-aware
%CAN, 5% nodes occupy 85-98% of the entire Cartesian
%space, and some nodes have to maintain 450-1500 neigh-
%bors. In Proximity routing, physical topology is not consid-
%ered when constructing the overlay.
In terms of our $3$ criteria, the approach fares as follows:
% Unable to identify nodes that are close to routers but it can reduce routing
% latency to far away node by approximately 50-75%.
% maintenance of node states, subscriptions and notifications need global
% overview of the overlay resulting in high control overhead
% Statically implemented sacrificing the decentralized nature of DHTs and
% thus poorly scaling. Also we can end up with a very large number of regions.
% Because of the fact that a peer may appear in multiple
% such maps we can conclude that additional traffic for probing and notifications
% renders the approach does not scalable.
low

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Mithos}
\emph{Mithos} \cite{WR2003} is a \p\ protocol which incorporates directed
incremental probing to find near optimal node placement and integrates
geographic layout and proximity routing overlay optimization methods.
%%AD in general some mention of the mismatch problem must be made right???
%%		so that a reasonable connection can be established...

The bootstrap phase of \emph{Mithos} starts with a subset 
of existing members as the initial set of candidates and 
while the closest nodes are detected by iterative
probing of the neighborhood, the candidate neighbor--list gets updated. 
To avoid local minima, \emph{Mithos} probes all the neighbors 
within a two-hop distance from the current minimum 
before concluding the process.

After finding its first neighbor, an 
% new-coming   %%AD overall the term new-coming is somewhat odd.. incoming? 
incoming peer is assigned 
an \emph{ID} using information gathered during 
the iterative neighbor selection phase. 
%%AD use SIMPLE sentences that are well structured to say what u want
Based on the two closest nodes found, along with these nodes neighbors and the corresponding
distances a system of virtual springs is set so that the tension of each spring
is inversely proportional to the distance. 
%%AD the above is impossible to read.. "based on,... along with... " NO!!!
%%AD I am not sure what you are talking about here - I mean below... rework
%%	and simplify.. 
The system is then left to settle,
and the state in which it settles is used for its \emph{ID}. 
The benefit of these synthetic coordinates are that
they are explicitly used as the node's \emph{ID}, 
and distance computations among nodes
can be done in \emph{ID} space without requiring physical measurements.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% upto here %%%%%%%%%%%%%%%%

The last step of the algorithm is the 
interconnection among neighbors. 
\emph{Mithos} uses a \emph{quadrant-based} mechanism in which 
each node establishes a link to the closest neighbor in each quadrant. 
%%AD what is the quadrant??? Hugh??? 
During forwarding, the next hop is performed towards a neighbor 
in the same quadrant of the final destination. 
An incoming node may not know of other neighbors in all
quadrants, therefore, the node first identifies neighbors in all quadrants
using a mechanism based on ideas similar to a perimeter walk~\footnote{Used in
the Greedy Perimeter Stateless Routing (\emph{GPSR}) protocol.}  %%AD ref??
and then improves the results using parallel path processing 
by taking into account further geometric properties of node relationships.
%%AD the above 5-6 lines sounds impressive but there is little help 
%%	for the average ignorant reader.. what is perimeter walk in 
%%	general? how quadrants are formed? What is their relationship?

One major limitation of \emph{Mithos} is that the protocol cannot effectively
handle dynamic arrivals and departures from the network. 
\cite{CCRK2004}~points out the extensive probing to determine 
distances and evaluates \emph{Mithos} results as less accurate
than those derived with \emph{GNP}~\cite{ng_gnp_2001}. 
%%AD what is GNP??? How did it "land" here???
%%
The latter has been also attributed by~\cite{WSS2005} to 
the iterative neighbor selection process which that is 
reportedly prone to premature termination at local minima.
%%
\cite{cox_vivaldi_2004} argues that elements of the protocol's
spring relaxation technique require a centralized implementation 
affecting \emph{Mithos} scalability.
%%AD rephrased what is below as above...
% Another point that has negative effect to the
% scalability of the algorithm is that parts of its spring relaxation technique
% require a centralized implementation~\cite{cox_vivaldi_2004}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In regard to the $3$ criteria, \emph{Mithos} stands as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It has very good results in reducing communication latency among peers but its
% efficiency is being constrained by the fact that the proximity is calculated
% at bootstrap, assigning virtual coordinates that are used throughout of a
% nodes life cycle and thus the overlay is not adapting to a high-churn
% environment.
medium &
% Incremental probing is applied in quadrants and in two-hop distance at each
% step that does not generate a lot o control overhead.
medium &
% It is constrained by the fact that the protocol does not respond to dynamic
% peer arrivals and departures
low
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{LAPTOP}
\emph{LAPTOP} \cite{WLH2007} organizes the overlay 
%%AD what is the nature of the "structure" overlay here???
into a tree-based hierarchy so that 
hops required during message routing be reduced and 
maintenance overhead be minimized.
A caching scheme is also used so as
to further lower routing table update costs. 
It is theoretically shown that 
\emph{LAPTOP} routing path length is bounded by $O(log_d(N))$ and node
joining and leaving in the overlay network is bounded by
$O(d*log_d(N))$ hops in a balanced overlay tree with $N$ representing the
number of nodes and $d$ the maximum degree of each node. 
\emph{LAPTOP} 
%% implements 
adopts the geographical layout approach  
and constructs its layout in a self-organizing and 
efficient fashion. 
The physical distances are estimated
with round trip times to a few existing nodes in the overlay network.
%%
Each node is assigned a dot-formatted address (e.g., 1.3.4). 
Each octet ranges from
$1$ to $d$.
%  where $d$ is the maximum degree of the nodes. 
%%AD this definition was provided just above.. 
The assignment process is done by appending a unique octet 
to the address of the parent of each node, while
the root node is assigned address $1$.

@@

called \emph{routing cache}, 
%%AD clarify - routing caches are the special entries OR the routing tables???

@@

Caching enables a node to forward a message to a better 

@@

%%AD rephrased what is below as above.. 
% In terms of overlay maintenance, \emph{LAPTOP}
% incorporates a simple \emph{heartbeat}-based technique 
% where each parent node is
% responsible for monitoring its children.

@@

\cite{KLKP2008} exploits $2$ routing techniques: 
\emph{proximity routing selection (PRS)} and 
\emph{proximity neighbor selection (PNS)}.
%%
In \emph{PRS}, the goal is to choose the best next hop while routing a message.
\emph{Plain old Kademlia} (\emph{POK}) always selects the closest--node 
with respect to the \emph{XOR} metric.
With \emph{PRS} in place however, \emph{Kademlia} may also choose 
the node that exhibits the smallest underlay metric cost; in this way, 
it balances a trade-off between the logical overlay and 
actual underlying distances.
%%AD rephrased as above.. the "underlay" I am not sure what it is...
%  but with proximity routing, Kademlia should also choose the node
% that exhibits the smallest underlay metric cost, balancing a trade-off between
% the overlay and underlay progress distances.
%%
In \emph{PNS}, on the other hand, the goal is to keep peers 
with the least contact cost in the routing table. 
%%AD WHAT is this "least contact cost"?? Sounds funny! CHECK
As \emph{Kademlia} continually learns about new
peers via incoming requests and an iterative lookup process, 
%%AD what is this iterative lookup process???
no specialized algorithm is required for searching for 
more cost-effective peers 
and the system simply goes for the best peers ``seen'' thus far.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{CHOord considering Proximity on IPv6 (CHOP6)}
\emph{CHOP6} \cite{MT2007} roughly estimates the proximity among
nodes by exploiting the {\sl IPv6} address format and if available, 
\emph{RTT} information.
The proximity estimation is achieved by introducing a $64$-bit 
\emph{ID} scheme in which
the least significant bits are the {\sl IPv6} global routing prefix.
Thus, a longest--prefix match scheme is established.
% enabling a longest prefix match scheme. 
%%AD check is the word "longest" is correct..
The protocol is designed based on the
observation that it is feasible to estimate a node's geographical location by
examining the upper $32$-bits of its {\sl IPv6} address. 
Moreover, similar to \emph{Chord}~\cite{stoica_chord_2001}, 
\emph{CHOP6} uses a finger table, whose entries hold
more than one candidate node.
%
%\paragraph{}
% There are three cases in which a node chooses the next hop according to
% information it possesses.
%\begin{itemize}
% \item When no information about RTT is available candidate next hops, the
%  sender just selects a node in the finger table entry which shares the longest
% prefix with the destination.
% \item There is another possibility that after some communication with other
%  nodes, the source node should know of the RTTs to some of the nodes in finger
% table entry. In this case, the source node chooses the one with the smallest
% RTT with probability $p$. If there is a node with no measured RTT then the
% sender can select such a node with probability $1 - p$
% \item In this last case the source node has already communicated with all
%  candidate node in the finger table entry. Thus, the node selects the node
% whose RTT is the smallest with probability $p$, the one with the second
% smallest with probability $q$ and so on, where $0 \leq \ldots < r < q < p < 1$
% and $p+q+r+\ldots \leq 1$
%\end{itemize}
%
With respect to the $3$ qualitative criteria, \emph{CHOP6} stands as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Simple approach that exploits proximity but it is coarse grained and thus not
% efficient.
low &
% Its static nature imposes low overhead to the network
low &
% IPv6 is still not widely applied and supported.
medium
\end{tabular}
}
\end{center}
%%AD how does CHOP6 helps with the mismatch problem??
% \subsubsection{T2MC}
\emph{T2MC} \cite{SLCGZ2008} uses traceroute logs to detect 
the boundaries of an autonomous system (\emph{AS}) and
cluster nearby peers; the objective here is to 
diminish the redundant multiple messages that may 
unnecessarily cross \emph{AS}-boundaries.
\emph{T2MC} uses a customized $k$-mean classification
algorithm with $k = 2$ to perform the classification 
and exploits the stable structure of the Internet routers 
to help guide the clustering in question. 
Even though {\sl traceroute}
provides detailed information about the network structure, 
it extensive use may create overhead on the overall network structure. 
In this respect, it is often the case that administrators 
disable {\sl traceroute} support on their routers.
The latter may affect \emph{T2MC}'s performance.
Although overall experimental results have been encouraging, 
\emph{T2MC} is considered coarse-grained
as it classifies peers into only ``remote'' and ``close''
groups \cite{QLZG2009}.
%%AD a better connection with the mismatch problem has to be made... 
%%		.. in the form of 1-2 lines (or short statements). 
%T2MC \cite{SLCGZ2008} uses trace-route logs to detect different autonomous
%systems and cluster close by peers, thus reducing redundant traffic that crosses
%autonomous system boundaries. T2MC uses a customized k-mean classification
%algorithm with $k=2$ to perform the classification, and exploits the stable
%structure of the Internet routers to guide clustering. The peer chooses the
%minimum and maximum Latency results from the trace-route to initialize the
%centroids of two sets. Then the peer calculates, for all hops along its
%trace-routed path, the peer calculates the absolute distance to these centroids
%of both sets and assigns the routers to that centroid with which it has the
%smaller absolute distance. After that, the mean and variance values are
%calculated and if the variance is larger than a predefined threshold then the
%algorithm sets the two latency mean values as new centroids for the two sets and
%loops again. Ultimately peer will end up with two sets having the minimum
%intra-set variance. The peer, then, chooses the router from the second set with
%the minimum hops attribute and sets it as a threshold. The selected router and
%all others whose hops attribute is larger than the threshold are classified as
%\emph{remote} router cluster. The remaining are classified as \emph{near}. From
%the near class, the peer chooses the one with maximum hops attribute as its edge
%router, and registers it along with all near clusters into the DHT of the
%\p\ overlay. As new peers join the network, those that share the same edge
%router or any of the members of the near router clusters, would form a close
%peer cluster. As Edge routers can provide more valuable information than other
%members of the near set, T2MC was designed to prioritize interaction of peers
%and edge gateways.
%The use of Trace-route as a tool for implementing the distance measuring
%infrastructure raise concerns about its efficiency and scalability. Being,
%primarily, a network diagnostic utility,
% Even though trace-route provides detailed information about the network
% structure, its excessive use creates additional overhead that stresses further
% the overall network infrastructure. This forces network administrators to
% disable its support from the routers they manage, thus jeopardizing the
% effectiveness of the T2MC algorithm.

>>>>

This section offers description and analysis of algorithms proposed
to address the topology mismatch problem in structured \p\ networks. 
The categorization of the approaches is based on how different
levels of proximity information is gathered as well as  
the way peer routing tables are maintained and used in an effort make hops in
overlays as efficient as possible. 
%%AD what does it really mean this below???
%%VM it means that this split into i) geographic layout, ii) proximity routing
%%   and iii) proximity neighbour selection types of algorithms are terms
%%   coined in those papers
The categorization is based on previous work found in the
literature~\cite{CDHR2002,CDCR2002,RSS2002}.

@@

%% VM Most of this paragraph on global soft-state rewritten/restructured.
%% Have a look...

\emph{Global Soft-State} \cite{XTZ2003} builds a global view to help nodes
choose shorter routing paths. To generate the proximity information, it 
combines the landmark binning method with small
scale distance probes to reveal the properties 
of the underlying network. 
%Figure \ref{fig:global_softstate} presents the landmark
%space and the mapping of the position of the nodes.

This global view of the network state is used by organizing it into ``maps'' for
regions of the overlay, that are strategically placed
across the network and made available to any node. The notion of a
region is a well defined property for structured \p\ networks and can be part of
the Cartesian space in overlays like \emph{eCAN}~\cite{xu_ecan_2002} or a set of
nodes sharing a particular prefix in overlays such as
\emph{Pastry}~\cite{antony_pastry_2001}. Moreover, a node may appear in a maximum
of $log(N)$ such maps.

Direct access to this information, also coined \emph{soft states}, helps nodes
find the best way to route their messages, while a publish/subscribe mechanism
allows them to get notified on dynamic network changes.

%%
Although this approach does reduce the routing latency to far nodes, it
can become expensive as it is 
possible to end up with a very large number of regions
each of which has to maintain a map. 
The fact that a peer may appear in multiple
such maps points into additional traffic for probing and notifications
and so renders the approach not scalable \cite{RGJZ2004}. 
Moreover, to refine measurements
additional inner-bin measurements are needed~\cite{WZS2004}.
Also, improvements within a region can be minimal as there exists
limited knowledge about neighboring zones.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% COMM Removed most of the paragraph below which 
%%		contains info that we cannot back
%%
%% Rescanned papers and wrote the paragraph below.
%% DO NOT PERMANENTLY DELETE!
%%
% Unfortunately, maintained of several host states at different layers,
% renders any content migration a costly process. Additionally, the method does
% not make any continuing effort to remap
% the overlay structure after nodes successfully join resulting into poor
% adaptation to changing conditions. Although this approach greatly reduces the
% routing latency to far nodes, it is unable to dynamically identify nodes that
% are close to routers and gateways in order to construct the secondary overlay.
% Nevertheless, static recognition of such nodes is currently done based on BGP
% reports and pre-chosen landmarks, sacrificing the self-organizing attribute of
% traditional DHTs.
%
%
% TODO: SOME DISCUSSION
%
% Xu \textit{et al.} \cite{XTZ2003} state that there are three ways
% generating proximity information
%\begin{itemize}
% \item Expanding Ring Search\\
%Expanding ring search can be of two forms. First it can utilize the multi-cast
%infrastructure in the underlying network in order to emit its messages.
%Unfortunately such infrastructures are not widely deployed thus the
%implementations of this way of generating proximity information is limited to
%blindly flooding the neighborhood to obtain reasonable results.
%
% \item Heuristics\\
%Heuristics are used in order to reduce the blindness of the expanding ring
%search and make realizations more efficient and effective. Unfortunately a
%common problem of all heuristic approaches is the local minimum pitfall in
%which
%the search might be caught into.
%
% \item Landmark Binning\\
%Landmark clustering is based on the view that nodes with similar distances to a
%set of predefined well-known landmark nodes are pretty likely of being close to
%each other. But this approach has its weaknesses as well, such as the fact that
%is a rather coarse grained approximation, therefore not particularly well
%suited
%for differentiating nodes within close distance to each other.
%
%\end{itemize}
%
%
%
% TODO: IN PAPER INTRODUCTION A DISCUSSION ABOUT
%TOPOLOGY-AWARE CAN
%
%Techniques to exploit topology information in overlay
%routing include geographic layout, proximity routing and
%proximity neighbor selection [3]. With geographic layout
%such as topology-aware CAN [12], the overlay structure is
%constrained by underlying network topology. This tech-
%nique, unfortunately, can create uneven distribution of
%nodes in the overlay, increasing the chances of overloading
%nodes and rendering the maintenance cost formidable. Our
%study shows that, for a typical 10,000-node topology-aware
%CAN, 5% nodes occupy 85-98% of the entire Cartesian
%space, and some nodes have to maintain 450-1500 neigh-
%bors. In Proximity routing, physical topology is not consid-
%ered when constructing the overlay.
%
In terms of our $3$ criteria, the approach fares as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Unable to identify nodes that are close to routers but it can reduce routing
% latency to far away node by approximately 50-75%.
medium &
% maintenance of node states, subscriptions and notifications need global
% overview of the overlay resulting in high control overhead
high &
% Statically implemented sacrificing the decentralized nature of DHTs and
% thus poorly scaling. Also we can end up with a very large number of regions.
% Because of the fact that a peer may appear in multiple
% such maps we can conclude that additional traffic for probing and notifications
% renders the approach does not scalable.
low
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Mithos}

%% VM Whole paragraph rewritten

%% VM: PREVIOUS COMMENTS BELOW REGARDING PREVIOUS VERSION
%%AD in general some mention of the mismatch problem must be made right???
%%		so that a reasonable connection can be established...
%%AD what is the quadrant??? Hugh???

%%AD ref?? (σ.σ. GPSR protocol)

%%AD the above 5-6 lines sounds impressive but there is little help 
%%	for the average ignorant reader.. what is perimeter walk in 
%%	general? how quadrants are formed? What is their relationship?

%%AD what is GNP??? How did it "land" here???

\emph{Mithos}~\cite{WR2003} ensures that neighbouring nodes in the overlay are
close also in terms of the underlying layer by integrating proximity layout
and proximity routing overlay optimizations.

During bootstrap, an incoming peer, say J, starts with a set of
candidates to establish links with and iteratively
probes for minimizing distances, based on a given metric (i.e., network delay)
and concluding when no further refinement can be achieved. To tackle the local
minima problem that such a gradient descent method suffers from, Mithos probes
all neighbours within a two-hop radius, from the currrent node that minimize
the distance, before concluding the process.

Next, the incomming peer is assigned a synthetic \emph{ID} that
represents the state of minimum distance from its close--by neighbourhood as
this was identified during the iterative neighbor selection phase described
above. The benefit of these synthetic coordinates is that distance computations
among nodes can be done in the \emph{ID} space without requiring physical
measurements. The actual link establishment with the peers, that will be J's
neighbours, is happening next. With peer J dividing the plane into four regions,
the \emph{quadrant-based} mechanism Mithos employs, suggests that the node
establishes a link to the closest neighbor in each quadrant of the plane. The
previous steps
do not provide any knowledge as to which nodes these would be, thus J has to
identify them. It does so, by starting from a known node in the neighbourhood
and scanning towards all quadrant borders ~\cite{KK2000,R2002}.

One major limitation of \emph{Mithos} is that the protocol cannot effectively
handle dynamic arrivals and departures from the network. 
\cite{CCRK2004}~argues about extensive probing to determine 
distances and less accurate proximity results compared to other
virtual coordinate systems. The latter has been also attributed
by~\cite{WSS2005} to the iterative neighbor selection process which that is 
reportedly prone to premature termination at local minima.
%%
\cite{cox_vivaldi_2004} argues that elements of the protocol's
synthetic ID generation require a centralized implementation 
affecting \emph{Mithos}' scalability.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In regard to the $3$ criteria, \emph{Mithos} stands as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It has very good results in reducing communication latency among peers but its
% efficiency is being constrained by the fact that the proximity is calculated
% at bootstrap, assigning virtual coordinates that are used throughout of a
% nodes life cycle and thus the overlay is not adapting to a high-churn
% environment.
medium &
% Incremental probing is applied in quadrants and in two-hop distance at each
% step that does not generate a lot o control overhead.
medium &
% It is constrained by the fact that the protocol does not respond to dynamic
% peer arrivals and departures
low
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{LAPTOP}
%
%%AD what is the nature of the "structure" overlay here???
%% VM the structure is that it is organized as a tree hierarchy.
\emph{LAPTOP} \cite{WLH2007} organizes the overlay 
into a tree-based hierarchy so that 
hops required during message routing be reduced and 
maintenance overhead be minimized.
A caching scheme is also used so as
to further lower routing table update costs. 
It is theoretically shown that 
\emph{LAPTOP} routing path length is bounded by $O(log_d(N))$ and node
joining and leaving in the overlay network is bounded by
$O(d*log_d(N))$ hops in a balanced overlay tree with $N$ representing the
number of nodes and $d$ the maximum degree of each node. 
\emph{LAPTOP} adopts the geographical layout approach  
and constructs its layout in a self-organizing and 
efficient fashion. 
The physical distances are estimated
with round trip times to a few existing nodes in the overlay network.
%%
Each node is assigned a dot-formatted address (e.g., 1.3.4). 
Each octet ranges from
$1$ to $d$.
The assignment process is done by appending a unique octet 
to the address of the parent of each node, while
the root node is assigned address $1$.

@@

@@

These special entries constitute the \emph{routing cache} which enables a node
to forward a message to a better 

@@

@@

\cite{KLKP2008} exploits $2$ routing techniques: 
\emph{proximity routing selection (PRS)} and 
\emph{proximity neighbor selection (PNS)}.
%%
In \emph{PRS}, the goal is to choose the best next hop while routing a message.
\emph{Plain old Kademlia} (\emph{POK}) always selects the closest--node 
with respect to the \emph{XOR} metric.
With \emph{PRS} in place however, \emph{Kademlia} may also choose 
the node that exhibits the smallest routing cost; in this way, 
it balances a trade-off between the logical overlay and 
actual underlying distances.
%%AD rephrased as above.. the "underlay" I am not sure what it is...
%  but with proximity routing, Kademlia should also choose the node
% that exhibits the smallest underlay metric cost, balancing a trade-off between
% the overlay and underlay progress distances.
%%
%% VM rephrased to not contain the word "underlay". Clean up comment block if OK.
%%
In \emph{PNS}, on the other hand, the goal is to keep peers 
with the least routing cost in the routing table. 
%%AD WHAT is this "least contact cost"?? Sounds funny! CHECK
%% VM rephrased to not contain the word "contact". Clean up comment block if OK.

%%
%% VM Commenting out since this info is not that important I believe
%%
%As \emph{Kademlia} continually learns about new
%peers via incoming requests and an iterative lookup process, 
%%%AD what is this iterative lookup process???
%no specialized algorithm is required for searching for 
%more cost-effective peers 
%and the system simply goes for the best peers ``seen'' thus far.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{CHOord considering Proximity on IPv6 (CHOP6)}

%%AD how does CHOP6 helps with the mismatch problem??
%% VM rewrote the whole part to answer this question
%% By and large, rtt measurements and id assignment help choose the next best
%% hop during routing that is i) toward the key and ii) has small cost
%% either in terms of explicit RTT or implicit RTT (taking regional/national
%% hops as a proxy of proximity - international RTT > regional RTT > national RTT)

\emph{CHOP6} \cite{MT2007} is another Chord-variant DHT; it exploits
the {\sl IPv6} address format, and if available \emph{RTT} information, to 
enable proximity estimation among peers during message routing.

Similar to \emph{Chord}~\cite{stoica_chord_2001}, 
\emph{CHOP6} uses a finger table but each entry now holds hold k>1 candidate
nodes. The next hop for a message is selected to be the one closest to the
destination among those k candidate nodes. This proximity is determined either
by exploiting RTT measurements or, if there is no such yet (i.e. a new peer), by
estimating distance on overlay's ID space. When joining the network, each node
receives a $64$-bit \emph{ID}. It comprises of a random part and a IPv6 prefix
part. The random part is obtained by hashing the node's IP address and port
number and is used to preserve the uniformity of
node assignment. The IPv6 prefix is based on IPv6's global routing prefix.
Because IANA  assigns address blocks to regions (RIRs) which are further
distributed on a national level (NIRs), examining the upper $32$-bits
of an IPv6 address someone can estimate the country or the region to which the
node is connected. Thus, CHOP6's IPv6 prefix ID is used for proximity estimation
if no RTT information is available during routing.

%
%\paragraph{}
% There are three cases in which a node chooses the next hop according to
% information it possesses.
%\begin{itemize}
% \item When no information about RTT is available candidate next hops, the
%  sender just selects a node in the finger table entry which shares the longest
% prefix with the destination.
% \item There is another possibility that after some communication with other
%  nodes, the source node should know of the RTTs to some of the nodes in finger
% table entry. In this case, the source node chooses the one with the smallest
% RTT with probability $p$. If there is a node with no measured RTT then the
% sender can select such a node with probability $1 - p$
% \item In this last case the source node has already communicated with all
%  candidate node in the finger table entry. Thus, the node selects the node
% whose RTT is the smallest with probability $p$, the one with the second
% smallest with probability $q$ and so on, where $0 \leq \ldots < r < q < p < 1$
% and $p+q+r+\ldots \leq 1$
%\end{itemize}
%
With respect to the $3$ qualitative criteria, \emph{CHOP6} stands as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Simple approach that exploits proximity but it is coarse grained and thus not
% efficient.
low &
% Its static nature imposes low overhead to the network
low &
% IPv6 is still not widely applied and supported.
medium
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{T2MC}

%%AD a better connection with the mismatch problem has to be made... 
%%		.. in the form of 1-2 lines (or short statements). 
%%
%% VM Added some extra lines and restructured the text
\emph{T2MC}'s~\cite{SLCGZ2008} objective is to diminish the redundant multiple
messages that may unnecessarily cross \emph{AS}-boundaries as these are the
links that cost more to ISPs thus minimizing the effects of the topology
mismatch problem. To achieve that, each node exploits the stable structure of
the Internet routers to help solve a clustering problem. Uses traceroute
logs to detect inter-\emph{AS} boundaries and clusters other peers to near-by and
far-away peers by applying a customized $k$-mean classification
algorithm with $k = 2$ to perform the classification.
Specifically when joining the network, the peer randomly picks an IP and uses
traceroute. Skipping the details of the algorithm, it picks the routers with
minimum and maximum latencies in the above traceroute path as initial centroids
for the ``near'' and ``remote'' sets respectively and after some iterations it
ends up with two sets having the minimum intra-set latency variance. The
router with the minimum hops in the ``remote'' set is set up as the hop
threshold and anything above that is classified as the ``remote'' router cluster
for that peer. Similarly, the router with the maximum hops in the ``near'' set
is important because it denotes an edge gateway. Peers that share the same
edge gateway or other members of the ``near'' router cluster are considered
close-by.
